Embodied Neuromorphic Benchmarks

### 2015-08-15 paper/paper.tex
Added references

This approach was first suggested in the context of evolutionary robotics.  
Notably, the problem faced by embodied neuromorphic benchmarking is remarkably 
similar to that faced earlier by these researchers. 
In evolutionary robotics, the
goal is to use genetic algorithms to \emph{evolve} systems that can control
robots to perform various tasks.  These tasks can be as simple as navigation
and obstacle avoidance, but have also included more difficult tasks such as walking,
object identification, and visual tracking [refs???].

However, performing evolution on real physical robots is problematic
for the same reasons that benchmarks on physical robots are problematic.  The
robots must be reset to the same state each time; they often involve
behaviour that can physically damage the robots; and they take a very long
time to run.  For this reason, attempts were made to evolve algorithms using simulated
robots.  However, the general finding was that algorithms that worked on the
simulated robots would not work when run on the real physical robots.  If
the simulations were improved, adding complex physical detail, then it was
possible to generalize to real behaviour; unfortunately, such complex
simulations would run slower than real-time [refs].

To address this problem, \cite{Jakobi97evolutionaryrobotics} proposed the creation of
``minimal'' simulations.  These are simulations where there is variability
\emph{within the simulation itself}.  In other words, we make \emph{poor}
simulations, but ensure that the way in which they are poor is itself
variable.  We are then in a position to ensure that the controllers work across that whole
range of variability.  ``Instead of trying to eliminate the differences between
simulation and reality, they are acknowledged, and mechanisms are put in place
to prevent evolving controllers from relying on them.'' [ref: jacobi thesis].

@@

It is worth noting that a minimal simulation only has to be a
good simulation \emph{for successful behaviour}.  That is, ``if we are evolving 
corridor following behaviour, the dynamics of the simulation might
differ wildly from those of reality if the controller hits a wall or
goes round in circles, but this does
not matter, since the controllers we are interested in transferring
across the reality gap will neither
hit walls nor go round in circles.''  [ref: jacobi thesis]  If the controller is poor, we do not 
need the simulation to be at all accurate in exactly \emph{how} that poor
behaviour is manifest.  We do not need an exact detailed physics model of
the collision between a robot and a wall, or a detailed model of what happens
to a robot arm when it starts oscillating wildly due to a poor control signal.
All we need is for the simulation to be just good enough to indicate that
things have gone wrong, and thus give a low score to that controller.  This
means that, for example, in a minimal simulation of an eight-legged walking robot,
it is not necessary to have a physics simulation that correctly models what
happens when two legs collide with each other.  Rather, if legs collide
with each other, that is an indication that the walking behaviour is very poor.
As long as that result is indicated we can greatly simplify the simulation
by not including all the details necessary to model these complex physical
interactions.

@@

Text Text Text Text Text Text  Text Text Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text. Text Text Text Text Text Text  Text Text Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text.

\textit{Funding\textcolon} Text Text Text Text Text Text  Text Text.

>>>>

This approach was first suggested in the context of evolutionary robotics.  
Notably, the problem faced by embodied neuromorphic benchmarking is remarkably 
similar to that faced earlier by these researchers. 
In evolutionary robotics, the
goal is to use genetic algorithms to \emph{evolve} systems that can control
robots to perform various tasks.  These tasks can be as simple as navigation
and obstacle avoidance, but have also included more difficult tasks such as walking,
collecting objects, and visual tracking (\citealt{Nolfi2000}).

However, performing evolution on real physical robots is problematic
for the same reasons that benchmarks on physical robots are problematic.  The
robots must be reset to the same state each time; they often involve
behaviour that can physically damage the robots; and they take a very long
time to run.  For this reason, attempts were made to evolve algorithms using simulated
robots.  However, the general finding was that algorithms that worked on the
simulated robots would not work when run on the real physical robots.  If
the simulations were improved, adding complex physical detail, then it was
possible to generalize to real behaviour; unfortunately, such complex
simulations would run slower than real-time (see \citealt{Husbands1992}; 
\citealt{Husbands1993}).

To address this problem, \cite{Jakobi97evolutionaryrobotics} proposed the creation of
``minimal'' simulations.  These are simulations where there is variability
\emph{within the simulation itself}.  In other words, we make \emph{poor}
simulations, but ensure that the way in which they are poor is itself
variable.  We are then in a position to ensure that the controllers work across that whole
range of variability.  ``Instead of trying to eliminate the differences between
simulation and reality, they are acknowledged, and mechanisms are put in place
to prevent evolving controllers from relying on them.'' \citep[p.~48]{jakobiThesis}

@@

It is worth noting that a minimal simulation only has to be a
good simulation \emph{for successful behaviour}.  That is, ``if we are evolving 
corridor following behaviour, the dynamics of the simulation might
differ wildly from those of reality if the controller hits a wall or
goes round in circles, but this does
not matter, since the controllers we are interested in transferring
across the reality gap will neither
hit walls nor go round in circles.''  \citep[p.~41]{jakobiThesis}  If the controller is poor, we do not 
need the simulation to be at all accurate in exactly \emph{how} that poor
behaviour is manifest.  We do not need an exact detailed physics model of
the collision between a robot and a wall, or a detailed model of what happens
to a robot arm when it starts oscillating wildly due to a poor control signal.
All we need is for the simulation to be just good enough to indicate that
things have gone wrong, and thus give a low score to that controller.  This
means that, for example, in a minimal simulation of an eight-legged walking robot,
it is not necessary to have a physics simulation that correctly models what
happens when two legs collide with each other.  Rather, if legs collide
with each other, that is an indication that the walking behaviour is very poor.
As long as that result is indicated we can greatly simplify the simulation
by not including all the details necessary to model these complex physical
interactions.

@@

We thank Andrew Mundy for extensive work on the Nengo SpiNNaker backend, and
James Knight for his SpiNNaker implementation of the learning rule used here.

\textit{Funding\textcolon} 
NSERC Discovery (grant 261453),
ONR (N000141310419)
AFOSR (FA8655-13-1-3084),
Canada Research Chairs,
and Canadian Foundation for Innovation
Ontario Innovation Trust.
